MassWateR: Improving quality control, analysis, and sharing of water quality data

### 2023-06-17 paper.Rmd
file requirements table added but woring with pdf render

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(MassWateR)
```

@@

The required data files for using are shown in table xx, including the steps in the workflow in Figure \@ref(fig:workflow) when a file is required.  The files are each imported into R using specific `read` functions with relevant checks, explained in the next section.  These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a potential.  Additionally, the `readMWRresultsview()` function...

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(MassWateR)
library(flextable)
library(here)

load(file = here('tabs/filerequirements.RData'))
```

@@

The required data files for using \CRANpkg{MassWateR} are shown in table xx, including the files that apply to the workflow steps in Figure \@ref(fig:workflow).  The files are each imported into R using specific `read` functions with relevant checks, explained in the next section.  These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a potential.  Additionally, the `readMWRresultsview()` function...

```{r}
filerequirements
```

### 2023-06-17 paper.tex
file requirements table added but woring with pdf render

The required data files for using are shown in table xx, including the steps in the workflow in Figure \ref{fig:workflow} when a file is required. The files are each imported into R using specific \texttt{read} functions with relevant checks, explained in the next section. These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a potential. Additionally, the \texttt{readMWRresultsview()} function\ldots{}

>>>>

The required data files for using \CRANpkg{MassWateR} are shown in table xx, including the files that apply to the workflow steps in Figure \ref{fig:workflow}. The files are each imported into R using specific \texttt{read} functions with relevant checks, explained in the next section. These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a potential. Additionally, the \texttt{readMWRresultsview()} function\ldots{}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{0.70in}|p{3.00in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}}

\ascline{1.5pt}{666666}{1-6}

\multicolumn{1}{>{\raggedright}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Formatted\ file}}}} & \multicolumn{1}{>{\raggedright}p{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Description}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{QC\ screening}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{QC\ reporting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{WQX\ formatting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Data\ analysis}}}} \\

\ascline{1.5pt}{666666}{1-6}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Results}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Water\ quality\ results\ organized\ by\ sample\ location\ and\ date}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-1.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-2.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-3.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-4.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{DQO\ accuracy}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Summary\ of\ data\ quality\ objectives\ that\ describe\ quality\ control\ accuracy\ for\ data\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-5.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-6.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-7.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-8.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{DQO\ frequency\ and\ completeness}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Summary\ of\ data\ quality\ objectives\ that\ describe\ quality\ control\ frequency\ and\ completeness\ measures\ for\ data\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-9.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-10.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Sites}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{A\ site\ metadata\ file,\ including\ location\ names,\ latitude,\ longitude,\ and\ additional\ grouping\ factors\ for\ sites\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-11.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-12.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-13.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{WQX\ metadata}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{A\ wqx\ metadata\ file\ required\ for\ generating\ output\ to\ facilitate\ data\ upload\ to\ WQX}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-14.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\

\ascline{1.5pt}{666666}{1-6}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}
